\selectlanguage{english}
\chapter*{English}

\section*{Installation}

Download the game from the official repository's\footnote{%
	\url{https://github.com/Groctel/cgpn-sg}
}
latest release or clone it to play the latest non-released version:

\begin{lstlisting}[language=sh]
git clone https://github.com/Groctel/cgpn-sg
\end{lstlisting}

You need to install the game's dependencies with either \texttt{npm} and \texttt{yarn} before running CGPN\@.
Any of these two commands will install the dependencies locally in a directory called \texttt{node\_modules}.
Run them from the game's top directory (where the \texttt{README.md} file is):

\begin{lstlisting}[language=sh]
npm install
yarn install
\end{lstlisting}

Run the game with the same command you did in the previous step substituting \texttt{install} with \texttt{start}:

\begin{lstlisting}[language=sh]
npm start
yarn start
\end{lstlisting}

This should automatically open your browser and start running the game.
If it doesn't, open it and go to \texttt{localhost:8080} to start playing.
Refresh the tab to restart the game.
To stop the game, press \texttt{\^{}C} in the terminal where the game server is running.

\section*{Controls}

This game is played using the classic \texttt{WASD} and mouse first person controls.
Use your mouse to rotate the camera from the player's point of view.
Use the following keys to move the player

\begin{itemize}
	\item
		\texttt{A}\textbf{:}
		Move the player to the left.
	\item
		\texttt{D}\textbf{:}
		Move the player to the right.
	\item
		\texttt{S}\textbf{:}
		Move the player backwards.
	\item
		\texttt{W}\textbf{:}
		Move the player forward.
	\item
		\texttt{SPACE}\textbf{:}
		Jump.
\end{itemize}

If it's the first time you're playing with this control scheme, place your left hand's ring finger over the \texttt{A} key, your ring finger over the \texttt{W} key and your index finger over the \texttt{D} key.
This will let you press the \texttt{S} key moving the ring finger towards you from the \texttt{W} key and easily reach the \texttt{SPACE} key with your thumb.

Use your mouse to alter the world to your liking:

\begin{itemize}
	\item
		\texttt{LEFT CLICK}\textbf{:}
		Remove a cube.
	\item
		\texttt{RIGHT CLICK}\textbf{:}
		Place a cube.
	\item
		\texttt{WHEEL SCROLL}\textbf{:}
		Cycle through held cubes.
\end{itemize}

Cubes will be destroyed and placed where the player is looking, guided by the crosshair at the center of the screen.
If you're too far from a cube you'll have to get closer to interact with it!
